Certified Symbolic Transducer with the Application of String Solver

### 2025-02-17 Paper/main.tex
remove unnecessary file

A more pragmatic approach involves the formalization of symbolic FAs [1] and FTs [2], wherein transition labels are symbolic and potentially infinite. While the formalization of symbolic FAs has been comprehensively explored in the work of [3], the formalization of symbolic FTs remains largely unexplored. This gap presents additional challenges in establishing the correctness and applicability of such formalizations.

@@

We first present a mathematical form of FTs, which is independent of Isabelle's formalization. 
The key is the label theory, which defines how do output labels generated from input labels.

@@

\begin{figure}[t]
	\begin{lstlisting}
record (|$'q,$||$~'a,$| |$'b$|) |$\mathbf{NFT}$| =
	|$\mathcal{Q}_T$| :: "|$'q$| set"
	|$\Delta_T$| :: "(|$'q,$||$~'a,$| |$'b$|) LTTS"
	|$\mathcal{I}_T$| :: "|$'q$| set"
	|$\mathcal{F}_T$| :: "|$'q$| set"
        |$\mathcal{M}$| :: "|$'b\Rightarrow 'a$| Tlabel"

@@

In order to prove this abstract definition of product operation's correctness, we firstly formalize the outputs of an NFT regarding the input of an NFA. Figure \ref{fig-def-output} has two definitions: (1) \texttt{outputE} extracts the output (second element) from a path. (2) \texttt{outputL} defines the set of all outputs of an NFT $\mathcal{T}$, when the input is in the  language $\mathcal{A}$.

@@

\end{document}

>>>>

A more pragmatic approach involves the formalization of symbolic FAs [1] and FTs [2], wherein transition labels are symbolic and potentially infinite. While the formalization of symbolic FAs has been comprehensively explored in the work of \cite{cpp/KanLRS22}, the formalization of symbolic FTs remains largely unexplored. This gap presents additional challenges in establishing the correctness and applicability of such formalizations.

@@

We first present a pure mathematical form of FTs \cite{VeanesHLMB12Transducer}, which is independent of Isabelle's formalization. 
The central concept is the label theory, which characterizes the process by which output labels are derived from input labels.

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
record (|$'q,$||$~'a,$| |$'b$|) |$\mathbf{NFT}$| =
	|$\mathcal{Q}_T$| :: "|$'q$| set"
	|$\Delta_T$| :: "(|$'q,$||$~'a,$| |$'b$|) LTTS"
	|$\mathcal{I}_T$| :: "|$'q$| set"
	|$\mathcal{F}_T$| :: "|$'q$| set"
        |$\mathcal{M}$| :: "|$'b\Rightarrow 'a$| Tlabel"

@@

In order to prove this abstract definition of product operation's correctness, we firstly formalize the outputs of an NFT regarding the input of an NFA. Figure \ref{fig-def-output} has two definitions: (1) \texttt{outputE} extracts the output (second element) from a path in the NFT. (2) \texttt{outputL} defines the set of all outputs of an NFT $\mathcal{T}$, when the input is in the  language $\mathcal{A}$.

@@

\bibliography{literature}
\end{document}
